Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-15 qpip0.tex
Fix typos

Protocol:
\begin{enumerate}
	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ on inputs $1^\lambda, 1^{1/\varepsilon}, x$.
	\item The prover prepares $\rho^{\otimes m}$.
	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}={sk_1,\ldots,sk_m}$, on inputs $1^\lambda$ and $\vec{h}$. It sends $\vec{pk}$ to the prover.
	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ on inputs $\vec{pk}$ and $\rho^{\otimes m}$, and sends it to the verifier.
	\item The verifier samples $r\xleftarrow{\$}[m]$ which is the copy to run Hadamard round for.
		For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$. It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
	\item The prover generates $\vec{a}$ on inputs $pk, c, \sigma$ and sends it back to the verifier.
	\item \label{step:multi-testing}
		The verifier computes the outcome for each round.
		If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
		Else, it outputs the result from the Hadamard round copy.
\end{enumerate}
\end{protocol}

@@

Since $\{c\}$ is drawn  from $e_i$ with uniformly random $i\in [m]$, we have 
$$ z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$ 
	where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin \Ethan{Typo} probabilities. Note that $z$ is "sub-normalized", i.e. $\tr (z)= \text{probability of getting accepted} \leq 1$.

>>>>

Protocol:
\begin{enumerate}
	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ on inputs $1^\lambda, 1^{1/\varepsilon}, x$. \Ethan{As in step A of proto B...}
	\item The prover prepares $\rho^{\otimes m}$. \Ethan{Same as last pt.}
	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, on inputs $1^\lambda$ and $\vec{h}$. It sends $\vec{pk}$ to the prover.
	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ on inputs $\vec{pk}$ and $\rho^{\otimes m}$, and sends it to the verifier.
	\item The verifier samples $r\xleftarrow{\$}[m]$ which is the copy to run Hadamard round for.
		For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$. It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
	\item The prover generates $\vec{a}$ on inputs $\vec{pk}, \vec{c}, \sigma$ and sends it back to the verifier.
	\item \label{step:multi-testing}
		The verifier computes the outcome for each round.
		If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
		Else, it outputs the result from the Hadamard round copy.
\end{enumerate}
\end{protocol}

\Ethan{TODO Fix proof notations. Like U0, U notations might've been undefined; see parallel rep paper}

@@

Since $\{c\}$ is drawn  from $e_i$ with uniformly random $i\in [m]$, we have 
$$ z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$ 
	where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin probabilities. Note that $z$ is "sub-normalized", i.e. $\tr (z)= \text{probability of getting accepted} \leq 1$.
